\bf{Software Complexities: Do System and Change Complexity Relate?}

### 2013-12-18 paper/paper.tex
Added timeseries plots

\author{Aldosary, Buthainah\\
\texttt{aldosa@encs.concordia.ca}}
\affil{Concordia University\\
 Montreal, Canada}

@@

A quantitative research methodology was used for this empirical study where the objective was to develop models pertaining to our research questions. The choice of this method is key as it provides a connection between the empirical observation and mathematical expressions of the quantitative relationships. 
The data used for this study was provided by Dr. Peter Rigby, namely from the Apache HTTP Server Project written in C. All measures were calculated at a particular version (commit) and the data was retrieved from June 18, 1999 - March 3, 2011; that is during a 12 year time period.However, no further information is given if this data includes header files or not. SQL scripts were written to extract data of system and change complexity measure that answer each of the research questions using PostgreSQL 9.3. The resulting data was then imported into RStudio for further analysis. Finally, Spearman's rank correlation coefficient matrix was deduced for each measure.

@@

>>>>

\author{Aldosary, Buthainah\\
\texttt{b_aldosa@encs.concordia.ca}}
\affil{Concordia University\\
 Montreal, Canada}

@@

A quantitative research methodology was used for this empirical study where the objective was to develop models pertaining to our research questions. The choice of this method is key as it provides a connection between the empirical observation and mathematical expressions of the quantitative relationships. 
The data used for this study was provided by Dr. Peter Rigby, namely from the Apache HTTP Server Project written in C. All measures were calculated at a particular version (commit) and the data was retrieved from June 18, 1999 - March 3, 2011; that is during a 12 year time period. However, no further information is given if this data includes header files or not. SQL scripts were written to extract data of system and change complexity measure that answer each of the research questions using PostgreSQL 9.3. The resulting data was then imported into RStudio for further analysis. Finally, Spearman's rank correlation coefficient matrix was deduced to answer each of our research questions.

@@

%Traditional Complexity timeseries
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{TradComplexityMeasuresPlot}
   \caption{Traditional Complexity Measures Timeseries }
   \label{fig:tct}
\end{figure}

%Change Complexity timeseries
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{ChangeComplexMeasuresPlot}
   \caption{Change Complexity Measures Timeseries }
   \label{fig:cct}
\end{figure}

%Change and Traditional Complexity timeseries
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{ChangeandTradPlot}
   \caption{Traditional and Change Complexity Measures Timeseries }
   \label{fig:TandCCT}
\end{figure}
